Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-30 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:30	23:09:09	(Sun30.Aug)

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{\emph{Determining LCA window type}: Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{\emph{Determining Kaiser parameter boundaries}: LCA images created with a large and equal size window database, but where the upper bounds for $\beta$ and $\phi$ is varied. The upper left image is equal to DAS with rectangular window. While \Fig{mvdr_selected_windows} suggests that an upper bound 
\newline
\emph{Upper bound $\beta$:}\hfill
\parbox[t]{.9\linewidth}{.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{.}
}\label{oversampling_mosaic_bounds}
\end{figure*}

>>>>

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{\emph{Determining LCA window type}: MVDR images with typical frequency responses chosen for various pixel regions.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\protect\\\hspace{\textwidth}
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{MVDR window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of an unsteered rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{\emph{Determining Kaiser parameter boundaries}: LCA images created with a large and equal size window database, but where the upper bounds for $\beta$ and $\phi$ is varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the distance from the maximum to the -3dB point of the anchor
\newline
\emph{Upper bound $\beta$:}\hfill
\parbox[t]{.89\linewidth}{Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests MVDR hardly choose windows with maximum sidelobe level lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.}\newline
\emph{Upper bound $\phi$:}\hfill
\parbox[t]{.89\linewidth}{As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution. }
}\label{oversampling_mosaic_bounds}
\end{figure*}
